Comparison of Terrain Following and Cut Cell Grids using a Non-Hydrostatic Model

### 2015-05-24 src/tf-cutcell-comparison/tf-cutcell-comparison.tex
produce article without figures

\begin{document}
\newcommand{\TODO}[1]{\textcolor{purple}{TODO: \emph{#1}}}

@@

\begin{figure*}
	\centering
	\includegraphics{../msc-publication-fig-meshes/fig-meshes.pdf}
	%
	\caption{Examples of (a) BTF, (b) SLEVE, and (c) a cut cell grid, showing cell edges in the lowest four layers.  The two dimensional grids are \SI{20}{\kilo\meter} wide and \SI{20}{\kilo\meter} high.  SLEVE parameters are specified in the resting atmosphere test in section~\ref{sec:results}\ref{sec:resting}.  The cut cell grid was created by intersecting the terrain surface with a regular grid as described in section~\ref{sec:grid}.}
	\label{fig:grid}
\end{figure*}

@@

\begin{figure*}
	\centering
	\includegraphics{../msc-publication-fig-advection-tracer/fig-advection-tracer.pdf}
%
	\caption{Horizontally advected tracer contours at \(t = \SI{0}{\second}\), \SI{5000}{\second} and \SI{10000}{\second} using (a) centred linear scheme on a BTF grid, the upwind-biased cubic scheme on (b) the cut cell grid, (d) the BTF grid, and (c) the fourth order scheme from \citet{schaer2002} on the BTF grid, with contour intervals every 0.1.  Errors on the BTF grid at \(t = \SI{10000}{\second}\) are shown for (e) the fourth order scheme from \citet{schaer2002}, and (f) the upwind-biased cubic scheme, with contour intervals every 0.01.  Negative contours denoted by dotted lines.  The terrain profile is also shown immediately above the $x$ axis.  Subfigures (c) and (e) produced using the modified version of the code from \citet{schaer2002}.}
	\label{fig:advection-tracer}
\end{figure*}

@@

\begin{figure}
	\centering
	\includegraphics{../msc-publication-fig-resting/fig-resting.pdf}
%
	\caption{Maximum spurious vertical velocity, \(w\) (\si{\meter\per\second}), in the resting atmosphere test with results on BTF, SLEVE, cut cell and regular grids using the model from \citet{weller-shahrokhi2014} which includes a curl-free pressure gradient formulation.}
	\label{fig:resting}
\end{figure}

@@

\begin{figure*}
	\centering
	\includegraphics{../msc-publication-fig-gravityWaves-theta/fig-gravityWaves-theta.pdf}
%
	\caption{Anomalies in potential temperature in the gravity waves test after 5 hours with a mountain height, \(h_0 = \SI{250}{\meter}\).  The central domain in the lowest \SI{12}{\kilo\meter} is shown on (a) the BTF grid, and (c) the cut cell grid.  The four lowest layers of each grid are shown for (b) BTF, and (d) cut cell grids, using a narrower potential temperature scale.  The results on the SLEVE grid (not shown) are qualitatively identical to results on the BTF grid.}
	\label{fig:gw-theta}
\end{figure*}

\begin{figure}
	\centering
	\includegraphics{../msc-publication-fig-gravityWaves-sampleLine/fig-gravityWaves-sampleLine.pdf}
%
	\caption{Vertical profiles of the Exner function of pressure, \(\Pi\), and potential temperature, \(\theta\), in the gravity waves test with a mountain height of \(h_0 = \SI{500}{\meter}\).  Exner profile is visually identical on all grids for both mountain heights; for clarity, the Exner profile is only plotted for the BTF grid.  The computational mode is manifested as a zig-zag in potential temperature on the cut cell grid which.   Results on the SLEVE grid (not shown) are qualitatively the same as those on the BTF grid.  The thermal profile with a lesser mountain height of \(h_0 = \SI{250}{\meter}\) (not shown) exhibits a computational mode with smaller amplitude.}
	\label{fig:gw-exner-theta}
\end{figure}

>>>>

\begin{document}

@@

\begin{figure*}
	\centering
%	\includegraphics{../msc-publication-fig-meshes/fig-meshes.pdf}
	%
	\caption{Examples of (a) BTF, (b) SLEVE, and (c) a cut cell grid, showing cell edges in the lowest four layers.  The two dimensional grids are \SI{20}{\kilo\meter} wide and \SI{20}{\kilo\meter} high.  SLEVE parameters are specified in the resting atmosphere test in section~\ref{sec:results}\ref{sec:resting}.  The cut cell grid was created by intersecting the terrain surface with a regular grid as described in section~\ref{sec:grid}.}
	\label{fig:grid}
\end{figure*}

@@

\begin{figure*}
	\centering
%	\includegraphics{../msc-publication-fig-advection-tracer/fig-advection-tracer.pdf}
%
	\caption{Horizontally advected tracer contours at \(t = \SI{0}{\second}\), \SI{5000}{\second} and \SI{10000}{\second} using (a) centred linear scheme on a BTF grid, the upwind-biased cubic scheme on (b) the cut cell grid, (d) the BTF grid, and (c) the fourth order scheme from \citet{schaer2002} on the BTF grid, with contour intervals every 0.1.  Errors on the BTF grid at \(t = \SI{10000}{\second}\) are shown for (e) the fourth order scheme from \citet{schaer2002}, and (f) the upwind-biased cubic scheme, with contour intervals every 0.01.  Negative contours denoted by dotted lines.  The terrain profile is also shown immediately above the $x$ axis.  Subfigures (c) and (e) produced using the modified version of the code from \citet{schaer2002}.}
	\label{fig:advection-tracer}
\end{figure*}

@@

\begin{figure}
	\centering
%	\includegraphics{../msc-publication-fig-resting/fig-resting.pdf}
%
	\caption{Maximum spurious vertical velocity, \(w\) (\si{\meter\per\second}), in the resting atmosphere test with results on BTF, SLEVE, cut cell and regular grids using the model from \citet{weller-shahrokhi2014} which includes a curl-free pressure gradient formulation.}
	\label{fig:resting}
\end{figure}

@@

\begin{figure*}
	\centering
%	\includegraphics{../msc-publication-fig-gravityWaves-theta/fig-gravityWaves-theta.pdf}
%
	\caption{Anomalies in potential temperature in the gravity waves test after 5 hours with a mountain height, \(h_0 = \SI{250}{\meter}\).  The central domain in the lowest \SI{12}{\kilo\meter} is shown on (a) the BTF grid, and (c) the cut cell grid.  The four lowest layers of each grid are shown for (b) BTF, and (d) cut cell grids, using a narrower potential temperature scale.  The results on the SLEVE grid (not shown) are qualitatively identical to results on the BTF grid.}
	\label{fig:gw-theta}
\end{figure*}

\begin{figure}
	\centering
%	\includegraphics{../msc-publication-fig-gravityWaves-sampleLine/fig-gravityWaves-sampleLine.pdf}
%
	\caption{Vertical profiles of the Exner function of pressure, \(\Pi\), and potential temperature, \(\theta\), in the gravity waves test with a mountain height of \(h_0 = \SI{500}{\meter}\).  Exner profile is visually identical on all grids for both mountain heights; for clarity, the Exner profile is only plotted for the BTF grid.  The computational mode is manifested as a zig-zag in potential temperature on the cut cell grid which.   Results on the SLEVE grid (not shown) are qualitatively the same as those on the BTF grid.  The thermal profile with a lesser mountain height of \(h_0 = \SI{250}{\meter}\) (not shown) exhibits a computational mode with smaller amplitude.}
	\label{fig:gw-exner-theta}
\end{figure}
